\section{Data}
This work uses trade data from Directions of Trade (DOTs). Our DOTS sample covers 157 countries for the period 1960-2017. Data on governance is from the World Bank governance indicators for 2000-2017. In particular, we consider the rule or law and political stability indicators. The literature emphasizes the importance of the rule of law in economic development \citep{Acemoglu2001, Acemoglu2002}, while political stability is important for our counterfactual scenarios. Formal bilateral political relationships, which enter bilateral trade costs in our model, are proxied by data on affinity of nations and ideal points difference \citep{Bailey2017EstimatingData}, and by data on formal defense alliances from the Correlates of War (COW) \citep{gibler2009cow}.


Bilateral gravity data are taken from the Centre D'Etudes Prospectives et D'Informations Internationales Gravity dataset (CEPII, see Head et al., 2010 for a detailed description of the data). FTA is a binary variable that takes value of 1 if a country-pair has an active FTA agreement in place and 0 otherwise.  Geographical characteristics and distances between countries are also from CEPII. Colony and contiguity dummy variables are used to control for pair-specific trade costs that are not directly related to distance. Furthermore, the dummy variable representing common legal origin captures the compatibility of the legal systems of trading partners as well as the trade costs related to the signing of contracts. The common spoken language and common religion dummy variables capture the effects of cultural similarities on trade \citep{Melitz2014}.
 
National accounts data are taken from version 9.0 of Penn World Tables \citep{Feenstra2014}. We use output-side real GDP at current PPPs (in mil. 2011US\$) to measure income, capital stock at current PPPs (in million 2011 US\$) to measure capital, and number of persons engaged (in millions) to measure labor endowment. We also use their measure of human capital.

